Exercise 2.1 Does \AE schylus understand \OE dipus?

Exercise 2.2 The smallest internal unit of \TeX is about 53.63 \AA.

Exercise 2.3 They took some honey and plenty of money wrapped up in a {\it\$}5 note.\par
Exercise 2.4 \'El\`eves, refusez vos le\c cons! Jetez vos cha\^\i nes!

Exercise 2.5 Za\u sto tako polako pijete \u caj?

Exercise 2.6 Mein Tee ist hei\ss.

Exercise 2.7 Peut-\^etre qu'il pr\'ef\`ere le caf\'e glac\'e.

Exercise 2.8 ?`Por qu\'e no bebes vino blanco? !`Porque est\'a avinagrado!

Exercise 2.9 M\'\i \'\j n idee\"en worden niet be\"\i nvloed.

Exercise 2.10 Can you take a ferry from \"Oland to \AA land?

Exercise 2.11 T\"urk\c ce konu\c san ye\u genler nas\i llar?

Exercise 2.12 I entered the room and---horrors---I saw both my father-in-law and my
mother-in-law.

Exercise 2.13 The winter of 1484--1485 was one of discontent

Exercise 2.14 His ``thoughtfulness'' was impressive.

Exercise 2.15 Frank wondered,``Is this a girl that can't say `No!'?''

Exercise 2.16 He thought, ``\dots and this goes on forever, perhaps to the last recorded syllable.''

Exercise 2.17 Have you seen Ms.~Jones?

Exercise 2.18 Prof.~Smith and Dr.~Gold flew from Halifax~N.~S. to Montr\'eal, P. Q. via Moncton,~N.~B


\tt Problem with German \ss

\font\sf = cmss10 scaled \magstep 2

\sf Exercise 2.20 Typeset a paragraph of magnified sans serif text

\font\pbkd = pbkd
\pbkd HEHE

\font\didot = didotb9r
\didot LALALALA

\font\cmr = cmr12
\cmr TRIAL \par

\font\cmrr = cmr10 scaled \magstep 1
\cmrr TRIAL 

\font\drfont = drmb14 
\drfont TRIAL

\bye
